### 2016-04-06 HSF-TN/draft-2016-VACPLAT/draft-HSF-TN-2016-VACPLAT.tex
Do not block 169.254.169.253!

Where possible, VMLMs should provide an approximation of OpenStack's 
environment for VMs, which is derived from EC2. Any contexualization 
user\_data file required and a metadata service should be provided via a 
``Magic IP'' 
HTTP service at 169.254.169.254 from the point of view of the VM. 
Monolithic VM images which do not use a user\_data file require a 
metadata service to be able to discover the 
URLs of the \texttt{\$MACHINEFEATURES}, \texttt{\$JOBFEATURES}, and 
\texttt{\$JOBOUTPUTS} locations.

@@

VMLMs must also support VMs which use Cloud Init contextualization.

>>>>

Where possible, an approximation of OpenStack's environment for VMs, which 
is derived from EC2, should be provided. Any contexualization 
user\_data file required and a metadata service should be provided via a 
``Magic IP'' 
HTTP service at 169.254.169.254 from the point of view of the VM. 
Monolithic VM images which do not use a user\_data file require a 
metadata service to be able to discover the 
URLs of the \texttt{\$MACHINEFEATURES}, \texttt{\$JOBFEATURES}, and 
\texttt{\$JOBOUTPUTS} locations.

@@

VMLMs must ensure they support VMs which use Cloud Init contextualization.

VMs must not block access to the address 169.254.169.253, which is used
by Amazon for DNS and by Vac for the default route, the local DNS, and 
for the Machine/Job Features HTTP service.
